Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/sim_details.tex
Minor edits.

We fix the sliding window size $M = 100$. We found that low values of $M$ induced too much random noise into the results, and further increasing $M$ did not make a substantial qualitative difference.

>>>>

We fix the sliding window size $M = 100$. We found that low values of $M$ induced too much random noise in the results, and increasing $M$ further did not make a substantial qualitative difference.
